\let\nofiles\relax % This is because res says to not emit aux files,
                   % but lastpage needs aux files.
\documentclass[margin,line]{res}
\usepackage[colorlinks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{amsmath,amssymb}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage[normalem]{ulem}

\oddsidemargin -.5in
\evensidemargin -.5in
\voffset -25pt
%\topmargin -.2in
\headsep 25pt
\textwidth=6.0in
\textheight=9.0in
\itemsep=0in
\parsep=0in

% Headings
\pagestyle{fancy}
\lhead{Yong Gao --- Curriculum Vitae}
\chead{}
\rhead{\thepage\ of \pageref*{LastPage}}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\newcommand{\myname}{Yong Gao --- Curriculum Vitae}
\newlength{\mynamewidth}
\settowidth{\mynamewidth}{\namefont\myname}

\name{\hspace*{0.5\textwidth}\hspace{-0.5\mynamewidth} \large{\myname}\vspace*{.1in}}
% On the first page, have no header.
\thispagestyle{empty}

\begin{resume}

\input{ContactContent.tex}

% \section{\sc Citizenship}
% United States

\section{\sc Education}
{\bf Ph.D. candidate, Physics,} Peking University, Beijing, China \hfill {\bf August 2018-Present}\\
\vspace*{-.1in}
\begin{itemize}
\item[ ] Thesis Advisor: Prof.\ Lijing Shao
\item[ ] Thesis Title: {\it Probing Structures of Neutron Stars with Gravitational Waves}
\end{itemize}

{\bf B.S., Physics,} Dalian University of Technology, Dalian, Liaoning Province, China \hfill {\bf July 2018}\\
\vspace*{-.1in}
\begin{itemize}
\item[ ] Degree conferred with honor.
\item[ ] Senior Dissertation Advisors: Prof.\ Renxin Xu and Prof.\ Chong Li
\item[] Dissertation Title: {\it The Electron Distributions of Strangelets in the Thomas-Fermi Model}
% \item[ ] G.P.A.: 3.8/4.0
\end{itemize}


\section{\sc Research Interests}

{\bf Understanding composition and state of matter inside neutron stars (NSs).} Modelling gravitational waves (GWs) from NSs: tidal/spin effects in binary NS and NS-black hole systems, global non-radial oscillations of NSs, mountains on NSs. Studying dynamics and observational consequences of free/forced precession of NSs. 

{\bf Testing strong-field gravity.} Modelling GW waveform from compact binaries and oscillating compact objects beyond general relativity. Constructing timing model and testing gravity with pulsar timing. Studying the structures of rotating, tidally-deformed, and oscillating NSs in alternative theories of gravity.



\section{\sc Honors and Awards}
{\bf Principal Scholarship,} Peking University \hfill {\bf 2022-2023}\\
\\
{\bf Tung Scholarship,} Peking University \hfill {\bf 2021--2022}\\
\\
{\bf Merit Student,} Peking University \hfill {\bf 2021--2022}\\
\\
{\bf The Second Prize for Oral Presentation,} Physics Five Universities \hfill {\bf April 2021}\\
\\
{\bf Vela Prize for Oral Presentation,} FAST/Future Pulsar Symposium 9 \hfill {\bf August 2020}\\
\\
{\bf National Scholarship,} Peking University \hfill {\bf 2019--2020}\\
% \\
% {\bf Merit Student,} Peking University \hfill {\bf 2019--2020}\\
\\
{\bf Excellent Teaching Assistant Award,} Peking University \hfill {\bf 2019--2020}\\
\\
{\bf Principal Scholarship,} Peking University \hfill {\bf 2018--2019}\\
\\
{\bf Learning Excellence Award (First Prize),} Dalian University of Technology \hfill {\bf 2015--2016}\\
\\
% {\bf National Encouragement Scholarship,} Dalian University of Technology \hfill {\bf 2015--2016}\\
% \\
% {\bf National Encouragement Scholarship,} Dalian University of Technology \hfill {\bf 2014--2015}\\
% \\
% Added to improve page breaks

\vspace{-1em}

\section{\sc Teaching Experience}

{\bf Teaching Assistant}, Peking University
\vspace*{.05in}
\begin{itemize}
  \item[ ] \href{http://friendshao.github.io/teaching/ced22/}{Electrodynamics (B)} \hfill {\bf Fall 2022}
\item[ ] \href{http://friendshao.github.io/teaching/phy21/}{General Physics I}, $^{*}${\small incl. Mechanics $\&$ Electromagnetism} \hfill {\bf Fall 2021}
\item[ ] \href{http://friendshao.github.io/teaching/thmech19/}{Theoretical Mechanics (A)}, {\small{\bf Excellent Teaching Assistant Award}} \hfill {\bf Fall 2019}
\end{itemize}

\section{\sc Co-advised Students}

{\bf Ph.D. Student}, Peking University
\vspace*{.05in}
\begin{itemize}
\item[] {\bf Hongbo Li}, co-advised with Prof. Lijing Shao and Prof. Renxin Xu 
\hfill {\bf 2021--present} \\
\vspace*{.05in}
{\it  Oscillations of neutron stars and gravitational-wave asteroseismology}
\end{itemize}
{\bf Undergraduate Students}, Peking University
\vspace*{.05in}
\begin{itemize}
\item[] {\bf Haoyang Qi}, co-advised with Prof. Lijing Shao
\hfill {\bf 2021-Present}\\
{\it Constraints on ultralight dark matter with pulsar timing}
\item[] {\bf Huimei Wang}, co-advised with Prof. Lijing Shao 
\hfill {\bf 2020-2021}\\
{\it Undergraduate Dissertation: The structure of neutron stars with anisotropic pressure}
\item[] {\bf Jingyuan Deng}, co-advised with Prof. Lijing Shao 
\hfill {\bf 2020-2021}\\
{\it Undergraduate Dissertation: Forced precession of neutron stars}
\item[] {\bf Zexin Hu}, co-advised with Prof. Lijing Shao
\hfill {\bf 2020-2021}\\
{\it Scalarized neutron stars in massive scalar-tensor gravity}
\end{itemize}

\section{\sc Computer Skills}
%{\bf Languages---}%
Proficient in {\sc Mathematica}, Python, and Matlab. Experience in C, Bash, and HPC.\\
Markup languages: \LaTeX, Markdown.

% {\bf Operating systems---}%
% Mac OS, Linux/*nix.

{\bf Code development---} Most contributions can be found at \url{https://github.com/GravYong}.

\section{\sc Professional Activities, Outreach, and Service}
{\bf KAGRA Collaboration}
\vspace*{.05in}
% \begin{itemize}
%   \item[] {Member of Compact Binaries Coalescence (CBC) Group} \hfill{\bf 2018--Present}
% \end{itemize}
\begin{itemize}
\item[] Member of KAGRA Future Strategy Committee (FSC) \hfill{\bf 2021--Present}
\end{itemize}

% {\bf Conference organizer}
% \vspace*{.05in}

{\bf Chair of conference session/group meeting}
\vspace*{.05in}
\begin{itemize}
\item[]
\href{https://gwwiki.icrr.u-tokyo.ac.jp/JGWwiki/KAGRA/KSC/FSC/FWG/1stMeeting}{KAGRA Future Working Group 1st Open Meeting} ({\it online}) \hfill {\bf November 2021}
\end{itemize}
\begin{itemize}
  \item[]
  {Chair of the }\href{https://kiaagravity.github.io}{\sc Kiaagravity group meeting}   \hfill {\bf 2020-2021}
  \end{itemize}

{\bf Journal referee}
\vspace*{.05in}
% \hspace*{1em}
\begin{itemize}
  \item[]
  Classical and Quantum Gravity (CQG)
  \hfill {\bf 2021-Present}
  \item[]
  Research in Astronomy and Astrophysics (RAA)
  \hfill {\bf 2021-Present}
  \item[]
  Science China Physics, Mechanics $\&$ Astronomy (SCPMA)
  \hfill {\bf 2021-Present}
\end{itemize}

% {\bf Participated Grants}
% \vspace*{.05in}\\
% \hspace*{1em}
% ???
% Twiddle this for spacing
% \newpage

\ifx\nopubs\undefined
\input{PubsContent.tex}
\else
%
\fi

\section{\sc Popular Science Articles}

\begin{etaremune}
  \item {\bf Y. Gao}, L. Shao, R.-X. Xu, (2019) \href{https://gravyong.github.io/files/BNS_Popular.pdf}{The waltz of a binary neutron star system} ({an article about GW170817, \it in Chinese}).
  \item {\bf Y. Gao}, (2022) \href{https://gravyong.github.io/files/NS_Structure_Popular.pdf}{The structures of neutron stars} ({an article about dense matter in neutron stars, \it in Chinese}).
  \item {\bf Y. Gao}, L. Shao, (2022) \href{https://www.ligo.org/science/Publication-O3bTGR/translations/science-summary-chinese-simplified.pdf}{Does Einstein's theory of gravity hold up to the latest \\
  LIGO/VIRGO/KAGRA observations?} ({\bf translated} from \href{https://www.ligo.org/science/Publication-O3bTGR/}{the English version}).
\end{etaremune}


\input{TalksContent.tex}

\newpage{}
% \vspace{0.1in}

\section{\sc References}
\vspace*{.05in}
\parbox{\textwidth}{%
{\bf Lijing~Shao,} Assistant Professor of Kavli Institute for Astronomy and Astrophysics, Peking University \\
K217, Kavli Institute for Astronomy and Astrophysics  \\
5 Yiheyuan Road, Haidian District \\
Beijing 100871, P. R. China \\
email: \href{mailto:lshao@pku.edu.cn}{lshao@pku.edu.cn} \\
office phone: \href{tel: 86-10-6275-8461}{ 86-10-6275-8461}}
\par
\parbox{\textwidth}{%
{\bf Renxin~Xu,} Professor of Physics, Peking University\\
2912, Science Teaching Building No.~2, Department of Astronomy\\
5 Yiheyuan Road, Haidian District \\
Beijing 100871, P. R. China \\
email: \href{mailto:r.x.xu@pku.edu.cn}{r.x.xu@pku.edu.cn} \\
office phone: \href{tel:86-10-6275-8631}{86-10-6275-8631}}
\par
\parbox{\textwidth}{%
{\bf David Ian Jones,} Professor of Mathematical Physics, University of Southampton\\
B54, West Highfield Campus\\
University Road, SO17 1BJ\\
Southampton, United Kingdom \\
email: \href{mailto:d.i.jones@soton.ac.uk}{d.i.jones@soton.ac.uk} \\
office phone: \href{tel:44-23-8059-4829}{44-23-8059-4829}}
\par
\parbox{\textwidth}{%
{\bf Gregory Desvignes,} Postdoctoral Researcher of Radio Astronomy, Max Planck Institute for Radio Astronomy\\
Auf dem Hügel 69\\
D-53121 Bonn, Germany\\
email: \href{mailto:gdesvignes.astro@gmail.com}{gdesvignes.astro@gmail.com}}
% office phone: \href{tel:44-23-8059-4829}{44-23-8059-4829}}

\end{resume}
\end{document}

% Local Variables:
% mode: latex
% End: